Pool Model - A Mathematical Framework for Modelling Bacterial Consortia in Food Science

### 2025-12-11 paper/pool_model.tex
Replace seconds units to hours

Then $[\mu_0]=\unit{V/s}$, $[N_t]=\unit{1/V}$, and $[\mu]= \unit{1/s}$.

@@

        All curves were calculated using the model (\ref{eq:ode_3pool_resource2}) with parameters $\mu=2.5~\mathrm{s}^{-1}$, $\omega'=0.1~\mathrm{s}^{-1}$, $N_t = 10^4$.
        The blue curve includes cell-death of the bacteria in the lag phase $\omega = 0.15~\mathrm{s}^{-1}$ and thus exhibits a small dip before its exponential growth.
        Other curves show the case of no bacteria dying $\omega=0~\mathrm{s}^{-1}$ and represent different lengths of lag phases: short $\lambda=10^{-2}~\mathrm{s}^{-1}$ (dark green), intermediate $\lambda=10^{-3}~\mathrm{s}^{-1}$ (light green) and long one $\lambda=10^{-4}~\mathrm{s}^{-1}$ (yellow). Note that the steady state for $N(t)$ and $D(t)$ is for this model $\lim_{t\to\infty} N(t)=0$ and $\lim_{t\to\infty} D(t)=N_t$, because of the depletion of the resource pool.

@@

        The curves represent no temperature shift (green), one temperature jump $\Delta T = 10^\circ C$ at time $t=4~\mathrm{s}$ (orange)

@@

        The parameters of the back-flow rate are $\zeta=1 s/K $ and $\delta=5~\mathrm{s}^{-1}$.
        The other model parameters are $\mu=2.5~\mathrm{s}^{-1}$, $\omega'=0.5~\mathrm{s}^{-1}$, $\beta=5~\mathrm{s}^{-1}$, $\lambda=10^{-2}~\mathrm{s}^{-1}$, $\omega = 0~\mathrm{s}^{-1}$ for each curve.

@@

        The red curve describes the growth of the bacteria $A$ ($N_A = L_A+G_A$) with model parameters $\lambda_A=10^{-2}~\mathrm{s}^{-1}$, $\mu_A=3.0~\mathrm{s}^{-1}$.
        The blue curve describes the growth of the bacteria $B$ ($N_B = L_B+G_B$) with model parameters $\lambda_B=5\cdot 10^{-2}~\mathrm{s}^{-1}$, $\mu_B=2.5~\mathrm{s}^{-1}$.

@@

        with production rate $\kappa=0.2~\mathrm{s}^{-1}$.
        The toxin $T_B$ causes the cell death of bacteria $A$ with rate constant $\omega = 0.2~\mathrm{s}^{-1}$.
        The red curve describes the growth of the bacteria $A$ ($N_A = L_A+G_A$) with model parameters $\lambda_A=10^{-2}~\mathrm{s}^{-1}$, $\mu_A=3.0~\mathrm{s}^{-1}$.
        The blue curve describes the growth of the bacteria $B$ ($N_B = L_B+G_B$) with model parameters $\lambda_B=5\cdot 10^{-2}~\mathrm{s}^{-1}$, $\mu_B=2.5~\mathrm{s}^{-1}$.

@@

Note that $[\tilde{\mu}]=\mathrm{s}^{-1}$.

>>>>

Then $[\mu_0]=\unit{V/h}$, $[N_t]=\unit{1/V}$, and $[\mu]= \unit{1/h}$.

@@

        All curves were calculated using the model (\ref{eq:ode_3pool_resource2}) with parameters $\mu=2.5~\mathrm{h}^{-1}$, $\omega'=0.1~\mathrm{h}^{-1}$, $N_t = 10^4$.
        The blue curve includes cell-death of the bacteria in the lag phase $\omega = 0.15~\mathrm{h}^{-1}$ and thus exhibits a small dip before its exponential growth.
        Other curves show the case of no bacteria dying $\omega=0~\mathrm{h}^{-1}$ and represent different lengths of lag phases: short $\lambda=10^{-2}~\mathrm{h}^{-1}$ (dark green), intermediate $\lambda=10^{-3}~\mathrm{h}^{-1}$ (light green) and long one $\lambda=10^{-4}~\mathrm{h}^{-1}$ (yellow). Note that the steady state for $N(t)$ and $D(t)$ is for this model $\lim_{t\to\infty} N(t)=0$ and $\lim_{t\to\infty} D(t)=N_t$, because of the depletion of the resource pool.

@@

        The curves represent no temperature shift (green), one temperature jump $\Delta T = 10^\circ C$ at time $t=4~\mathrm{h}$ (orange)

@@

        The parameters of the back-flow rate are $\zeta=1 s/K $ and $\delta=5~\mathrm{h}^{-1}$.
        The other model parameters are $\mu=2.5~\mathrm{h}^{-1}$, $\omega'=0.5~\mathrm{h}^{-1}$, $\beta=5~\mathrm{h}^{-1}$, $\lambda=10^{-2}~\mathrm{h}^{-1}$, $\omega = 0~\mathrm{h}^{-1}$ for each curve.

@@

        The red curve describes the growth of the bacteria $A$ ($N_A = L_A+G_A$) with model parameters $\lambda_A=10^{-2}~\mathrm{h}^{-1}$, $\mu_A=3.0~\mathrm{h}^{-1}$.
        The blue curve describes the growth of the bacteria $B$ ($N_B = L_B+G_B$) with model parameters $\lambda_B=5\cdot 10^{-2}~\mathrm{h}^{-1}$, $\mu_B=2.5~\mathrm{h}^{-1}$.

@@

        with production rate $\kappa=0.2~\mathrm{h}^{-1}$.
        The toxin $T_B$ causes the cell death of bacteria $A$ with rate constant $\omega = 0.2~\mathrm{h}^{-1}$.
        The red curve describes the growth of the bacteria $A$ ($N_A = L_A+G_A$) with model parameters $\lambda_A=10^{-2}~\mathrm{h}^{-1}$, $\mu_A=3.0~\mathrm{h}^{-1}$.
        The blue curve describes the growth of the bacteria $B$ ($N_B = L_B+G_B$) with model parameters $\lambda_B=5\cdot 10^{-2}~\mathrm{h}^{-1}$, $\mu_B=2.5~\mathrm{h}^{-1}$.

@@

Note that $[\tilde{\mu}]=\mathrm{h}^{-1}$.
